The relativistic capture of compact objects by intermediate-mass black holes

### 2019-04-19 mn.tex
added paragraph about rates for LISA, ET, LIGO/Virgo etc

\begin{abstract}
%
% Motivation: Why do we care about the problem and the results?
% ==============================================================
%

%
% Problem statement: What problem are we trying to solve?
% ========================================================
%

%
% Approach: How did we go about solving or making progress on the problem?
% =========================================================================
%

%
% Results: What's the answer?
% ===========================
%

%
% Conclusions: What are the implications of our answer?
% ======================================================
%
\end{abstract}

@@

>>>>

\begin{abstract}
%
% Motivation: Why do we care about the problem and the results?
% ==============================================================
%
The gravitational capture of a stellar-mass compact object by a 
massive black hole constitutes a unique a probe of spacetime in the
strong regime of gravity.
%
% Problem statement: What problem are we trying to solve?
% ========================================================
%
Intermediate-mass black holes (IMBHs) with masses between $10^2$ and
$10^4\,M_{\odot}$ are probably lurking in globular clusters, but we still lack
observational evidence.  The detection of the gravitational waves of an
intermediate-mass ratio inspiral (IMRI) are twofold. First, a proof that black
holes exist in that mass range, necessary to understand how supermassive black
holes gained their masses.  Second, we can map spacetime and extract the
redshifted parameters with high precision.
%
% Approach: How did we go about solving or making progress on the problem?
% =========================================================================
%
Because IMBHs are not fixed at the centre of the cluster, to address the
formation and evolution of IMRIs analytically is very challenging, and the
problem requires numerical simulations. We present a detailed study of the
parameter space of IMRIs in globular clusters using a high-accurate,
direct-summation integrator.
%
% Results: What's the answer?
% ===========================
%
XXX
%
% Conclusions: What are the implications of our answer?
% ======================================================
%
YYY
Moreover, we estimate that a Milky Way-like galaxy should have an IMRI event rate of approximately
$5\times 10^{-4}\,\textrm{yr}^{-1}$.
\end{abstract}

@@

\pau{Dovremmo calcolare il tasso per LISA, ET, LIGO/Virgo... e' semplice... solo bisogna calcolare quante galassie ci sono
nel loro volume di osservazione e prendere una relazione come quella di Mc Laughlin. Prendiamo la distanzia all'orizzonte,
calcoliamo quante galassie ci sono e moltiplichiamo da 0.25:
\cite{McLaughlin99} derives a formation efficiency of cluster formation of
$\epsilon \equiv M_{GCs}/M_{\rm gas}$, with $M_{GCs}$ the initial
population of globulars and $M_{\rm gas}$ the available gas in the
protogalaxy. By evaluating a sample including giant ellipticals, faint dwarfs
and brightest cluster galaxies, the author obtains $\epsilon \simeq 0.25\%$,
and we note that the results are almost identical for the Population II
spheroid of the Milky Way.}
